### 2014-03-02 thesis/src/chapters/chapter-state-of-the-art.tex
Thesis: provider comparision

% radek
\section{Providers comparison}
In this section we would like to compare all depicted providers as well as other solution in terms of \emph{adaptivity} and \emph{scalability} as none of the examined providers support \emph{cloud federated} deployments. Table \ref{tab:cloud-providers-scaling} presents a summary of cloud providers auto-scaling capabilities. Interestingly, all of them are focused solely on horizontal scaling, ignoring advantages offered by a fine-grained approach to scaling that leverage scaling up and application tuning. Table \ref{tab:cloud-providers-adaptivity} summarises platforms approach to adaptivity: their data analysis mechanisms and policies support.

\begin{table}[!htbp]
\begin{tabularx}{\textwidth}[]{ X  X  X  X}
\specialrule{.1em}{.05em}{.05em}

  & \textbf{Horizontal scaling} & \textbf{Vertical scaling} & \textbf{Application tuning} \\
\specialrule{.1em}{.05em}{.05em}

\multicolumn{4}{ l }{\textbf{Infrastructure provider}} \\
\specialrule{.1em}{.05em}{.05em}

Carina & \checkmark & $\times$ & $\times$ \\ \hline

OneFlow & \checkmark & $\times$ & $\times$ \\ \hline

AWS EC2 & \checkmark & $\times$ & $\times$ \\ \hline

\multicolumn{4}{ l }{\textbf{Platform provider}} \\
\specialrule{.1em}{.05em}{.05em}

CloudFoundry & $\times$ & $\times$ & $\times$ \\ \hline

OpenShift & \checkmark & $\times$ & $\times$ \\ \hline

AppEngine & \checkmark & $\times$ & $\times$ \\ \hline

Azure & \checkmark & $\times$ & $\times$ \\ \hline

Heroku & $\times$ & $\times$ & $\times$ \\ \hline
\end{tabularx}

\caption{Comparison of cloud providers scaling capabilities}
\label{tab:cloud-providers-scaling}

@@

AWS EC2 & 
-- time frame based

-- expression based, where expressions corresponds to a AutoScalingGroup

-- actions are triggered by a CloudWatch alarms

-- customizable adjustments paddings, types, cooldown time
&
-- threshold model, takes into account minimal and maximal permitted instances of an application as well as application priority
\\ \hline

@@

AppEngine &

-- built-in policy based on request queue length

-- adjustable minimal, maximal number of application instances, pending latency

 &
-- queue-based, new instance is provisioned if queue length got too long 
  \\ \hline

Azure & 
-- time frame based

-- expression based, where expression can involve either CPU usage or Queue length

-- customizable adjustments paddings, types, cooldown time
&
-- threshold model, that takes into account minimal and maximal allowed instances
 \\ \hline

Heroku & $\times$ & $\times$ \\ \hline
\end{tabularx}

>>>>

% radek
\section{Providers comparison}
In this section we would like to compare all depicted providers in terms of fulfilling functional requirements specified in the overview. Table \ref{tab:cloud-providers-adaptivity} takes more detailed approach and summarises how platform tackles adaptivity: their data analysis mechanisms and policies support.

\begin{table}[!htbp]
\begin{tabularx}{\textwidth}[]{ l  X  X  X  X }
\specialrule{.1em}{.05em}{.05em} 
& \textbf{Carina} & \textbf{OneFlow} & \textbf{CloudFoundry} & \textbf{OpenShift} \\
\specialrule{.1em}{.05em}{.05em}

\textbf{Service operations} &  &  &  \\ \specialrule{.1em}{.05em}{.05em} 
Deploy a service & \checkmark  & \checkmark & \checkmark & \checkmark\\ \hline
Cancel the service & \checkmark & \checkmark & \checkmark & \checkmark \\ \specialrule{.1em}{.05em}{.05em}

\textbf{Status check} &  &  &  \\ \specialrule{.1em}{.05em}{.05em} 
Deployment success & \checkmark & \checkmark &  \checkmark & \checkmark \\ \hline
Uptime & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
Current cost & $\times$ & $\times$ & $\times$ & $\times$ \\ \specialrule{.1em}{.05em}{.05em}

\textbf{Client application} &  &  &  \\ \specialrule{.1em}{.05em}{.05em} 
CLI & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
Web service & $\times$ & $\times$ & \checkmark & \checkmark \\ \specialrule{.1em}{.05em}{.05em}

\textbf{Deployment descriptor} &  &  &  \\ \specialrule{.1em}{.05em}{.05em} 
Service name & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
Technology stack & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
Scaling policies & \checkmark & \checkmark & $\times$ & $\times$ \\ \specialrule{.1em}{.05em}{.05em}

\textbf{Deployment cost minimisation} & $\times$ & $\times$ & $\times$ & $\times$ \\ \specialrule{.1em}{.05em}{.05em}

\textbf{Self-adaptation and scaling} &  &  &  \\ \specialrule{.1em}{.05em}{.05em} 
Application platform tuning & $\times$ & $\times$ & $\times$ & $\times$ \\ \hline
Vertical scaling & $\times$ & $\times$ & $\times$ & $\times$ \\ \hline
Horizontal scaling & \checkmark & \checkmark & \checkmark & \checkmark \\ \hline
Multiple provider based scaling & $\times$ & $\times$ & $\times$ & $\times$ \\ \specialrule{.1em}{.05em}{.05em}

\end{tabularx}

\caption{Comparison of cloud providers features}
\label{tab:cloud-providers-comparision-features}

@@

@@

\end{tabularx}
